%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    { Senior Software Developer } % Job title
    {One97 Communications ltd.} % Organization
    {Noida, India} % Location
    {December 2019 - PRESENT} % Date(s)
    {
        \begin{cvitems} % Description(s) bullet points
        \item { Requirement discussion with Product Managers.}
        \item { Feature Breakdown and High level Design.}
        \item { Task Assignment and Mentoring.}
        \item { Developed  merchant onboarding flow for new services.}
        \item { Worked on Platform ACL}
        \item { implemented  circuit breaker,message broker and other pattern  . }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    { Software Developer } % Job title
    {Onmobile Global} % Organization
    {Bangalore, India} % Location
    {July 2018 - December 2019} % Date(s)
    {
        \begin{cvitems} % Description(s) bullet points
        \item { Developed Licence Server component of DRM for in-house Content Streaming Engine .}
        \item { Worked on Do Not Disturb Service.}
        \item { Worked on DNCTO Service. }
        \item { Worked on In-house Content Suggestion and content pushing  Product. }
        \item { Developed Report Modules for various Products.}
      \end{cvitems}
    }

%---------------------------------------------------------
  %---------------------------------------------------------
  \cventry
    { Software Engineer - Trainee} % Job title
    {Nextgen Healthcare} % Organization
    {Bangalore, India} % Location
    {Aug. 2017 - July 2018} % Date(s)
    {
        \begin{cvitems} % Description(s) bullet points
        \item { Worked on Health Quality Measures for 7 Months.}
        \item { Transformation of ASP Controls Reports to React pages. }
        \item { Developed Web Services for various Reports.}
        \item { constructed Stored Procedure for various Reports.}
        \item { Worked on QRDA IMPORT and EXPORT.}
        \item { Automated Unit Testing for QRDA IMPORT and EXPORT } 
        \item { Supported Patient Portal and EPM for 3 months} 
      \end{cvitems}
    }

%---------------------------------------------------------
  
%---------------------------------------------------------
\end{cventries}
